### 2022-05-01 article/main.tex
create develop branch

% !TEX program = XeLaTeX
\documentclass[12pt,ansiapaper]{article}

@@

% English
\usepackage[english]{babel}
\usepackage[english]{isodate}
\cleanlookdateon

@@

% Hypersetup
\hypersetup{
  linkcolor=Mahogany,
  citecolor=Mahogany,
  urlcolor=darkblue, 
  breaklinks=true, 
  colorlinks=true,
      pdfauthor={Danilo Freire; David Skarbek},
      pdfkeywords={Brazil, crime, extralegal violence, lynching, vigilantism},
  }

@@

% Author
\author{Danilo Freire\footnote{School of Social and Political Sciences, University of Lincoln, \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}}, \url{https://danilofreire.github.io}.} \and David Skarbek\footnote{Department of Political Science and the Political Theory Project, Brown University, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \url{http://davidskarbek.com}.}}

% Date
\date{June 16, 2021}

@@

Although lynchings and mob violence more generally have decreased in advanced democracies, it remains widespread in many parts of the world. Based on US State Department reports, \citet[33]{jung2020lynching} find that between 1976 and 2018, lynchings occurred in all regions of the world and in more than a hundred countries. In particular, Latin America has been severely affected by a recent increase in lynchings. Such a surge in citizen-led violence has reportedly been motivated by growing numbers of drug-related crimes and by police ineffectiveness \citep{mallen2014vigilantes}. Brazil provides a telling example. From 2011 to 2015, the country registered about 2,500 lynching episodes. In 2015, 173 people were killed by angry mobs---nearly one execution every two days \citep{barbara2015vigilantes, oliveira2016mob}. According to José de Souza Martins \citeyearpar{martins2015linchamentos}, who has studied lynchings in Brazil for more than thirty years, these figures are not only the highest in the country's history, but among the highest in the world. The people who participate in lynchings are typically  young men, but they also sometimes include teenage women and girls, elderly women, and even members of the local police \citep{moura2017linchamentos}.\footnote{Brazilian police forces in São Paulo kill hundreds of people every year in a way that looks similar to vigilantism \citep{willis2015killing}. Recent work also documents how organized crime groups in Brazil use extralegal violence in the process of governing favelas extralegally \citep{magaloni2020killing}.}

>>>>

% !TEX program = XeLaTeX
\documentclass[12pt,a4paper]{article}

@@

% English
\usepackage[english]{babel}
% \usepackage[english]{isodate}
% \cleanlookdateon

@@

% Hypersetup
\hypersetup{
  linkcolor=Mahogany,
  citecolor=Mahogany,
  urlcolor=darkblue, 
  breaklinks=true, 
  colorlinks=true,
      pdfauthor={},
      pdfkeywords={Brazil, crime, extralegal violence, lynching, vigilantism},
  }

@@

% Author
\author{Danilo Freire\footnote{School of Social and Political Sciences, University of Lincoln, \href{mailto:dfreire@lincoln.ac.uk}{\texttt{dfreire@lincoln.ac.uk}}, \url{https://danilofreire.github.io}.} \and David Skarbek\footnote{Department of Political Science and the Political Theory Project, Brown University, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \url{http://davidskarbek.com}.}}

% Date
\date{\today}

@@

Although lynchings and mob violence more generally have decreased in advanced
democracies, it remains widespread in many parts of the world. Based on US
State Department reports, \citet[33]{jung2020lynching} find that between 1976
and 2018, lynchings occurred in all regions of the world and in more than a
hundred countries. In particular, Latin America has been severely affected by a
recent increase in lynchings \citep{godoy2004justice, kloppe2020vortex}.
Such a surge in citizen-led violence has reportedly been motivated by growing
numbers of drug-related crimes and by police ineffectiveness
\citep{mallen2014vigilantes}. Brazil provides a telling example. From 2011 to
2015, the country registered about 2,500 lynching episodes. In 2015, 173 people
were killed by angry mobs---nearly one execution every two days
\citep{barbara2015vigilantes, oliveira2016mob}. According to José de Souza
Martins \citeyearpar{martins2015linchamentos}, who has studied lynchings in
Brazil for more than thirty years, these figures are not only the highest in
the country's history, but among the highest in the world. The people who
participate in lynchings are typically young men, but they also sometimes
include teenage women and girls, elderly women, and even members of the local
police \citep{moura2017linchamentos}.\footnote{Brazilian police forces in São
  Paulo kill hundreds of people every year in a way that looks similar to
vigilantism \citep{willis2015killing}. Recent work also documents how organized
crime groups in Brazil use extralegal violence in the process of governing
favelas extralegally \citep{magaloni2020killing}.}
